Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Split the countries before counting their unique occurrences

```{r}
countries_studied_by_count <- data_without_fmd %>% 
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = TRUE)

>>>>

```{r}
countries_studied_by_count <- data_without_fmd %>% 
  separate_rows(country_studied, sep = " ") %>%
    distinct(title, country_studied, .keep_all = TRUE) %>% 
    count(collab_type, country_studied, name = 'num_of_studies', sort = TRUE)
